Thank You, Next

### 2022-07-26 Manuscript/manuscript_draft.tex

\section*{Context/Introduction}
BASELINE OF MUTUALISMS
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences.

PAIRWISE VS MULTISPECIES

There are benefits of mutualistic interactions, but there are costs as well, some direct and some indirect. 
Directly, mutualistic partners can sometimes become parasitic, causing harm to the focal mutualist\cite{Bronstein2001a}. 
\tom{More indirectly, these interactions require energy.}{Awkward sentence, and I'm not sure why investment is reward is an indirect cost.} 
\tom{Within a mutualism, each participant offers rewards and in return receives benefits from their partners.}{No new information content in this sentence.} 
These rewards come in many forms (nectar, protection, habitat, etc.), all of which require some investment \cite{Bronstein2001}. 
These investments can be seen as the costs of mutualisms, they are traded for the rewards provided by a partner. 
\tom{Because of these trade-offs}{trade-offs between what and what?}, there are both costs and benefits to a mutualistic interaction\cite{Bronstein2001,Bronstein2001a}, \tom{particularly as the mutualism becomes more complex in the context of its environment}{I don't know what this means.}.\tom{}{Having made it to the end of this paragraph I can't really find any new information here. You are covering very basic aspects of mutualism that were already described in the first paragraph. I would get to the question/problem at the core of this paper more quickly.}

>>>>

\section*{Context/Introduction}
BASELINE OF MUTUALISMS
Mutualisms are species interactions in which all involved participants benefit. They are among the most widespread species interactions\cite{Chamberlain2014,Stachowicz2005,BoucherDouglasH.1985} with diverse and dynamic consequences. 
The benefits from these interactions are called rewards, but they require investment of resources into the interaction {I'm honestly not sure if I need to explain this idea?}.

PARTNER DIVERSITY IN MUTUALISMS

Historically, scientists focused on pairwise mutualisms *** citations ***, however, multi-species mutualisms are becoming better studied

There are benefits of mutualistic interactions, but there are costs as well, some direct and some indirect. 
Directly, mutualistic partners can sometimes become parasitic, causing harm to the focal mutualist\cite{Bronstein2001a}. 
\tom{More indirectly, these interactions require energy.}{Awkward sentence, and I'm not sure why investment is reward is an indirect cost.} 
These rewards come in many forms (nectar, protection, habitat, etc.), all of which require some investment \cite{Bronstein2001}. 
These investments can be seen as the costs of mutualisms, they are traded for the rewards provided by a partner. 
\tom{Because of these trade-offs}{trade-offs between what and what?}, there are both costs and benefits to a mutualistic interaction\cite{Bronstein2001,Bronstein2001a}, \tom{particularly as the mutualism becomes more complex in the context of its environment}{I don't know what this means.}.\tom{}{Having made it to the end of this paragraph I can't really find any new information here. You are covering very basic aspects of mutualism that were already described in the first paragraph. I would get to the question/problem at the core of this paper more quickly.}
